A thermodynamic view of dusty protoplanetary disks

### 2017-08-03 model.tex
misc minor edits

%\subsection{Dusty buoyancy forces}
We can now define the vertical buoyancy frequency $N_z$ of the mixture
as    
%$N_z$ of the mixture is given by 
\begin{align}
  N_z^2 \equiv - \frac{1}{\rho}\frac{\p P}{\p z}\frac{\p \seff}{\p z}
  =c_s^2(r) \frac{\p \ln{\rhog}}{\p z}\frac{\p \tepsilon}{\p z},
%  \quad 
 % N_z^2 \equiv - \frac{1}{\rho}\frac{\p P}{\p z}\frac{\p \seff}{\p z}.
%&=
  %\frac{c_s^2(r)}{\left(1+\epsilon\right)^2}\frac{\p\ln\rhog}{\p 
%  z}\frac{\p\epsilon}{\p z} \\ &
  %                                =
 % \frac{\epsilon}{\left(1+\epsilon\right)^2}\left(\frac{z}{\Htilde}\right)^2\OmK^2\notag,  
\end{align}
%Typically in a thin, smooth disk we have $|N_r|\ll |N_z|$. 
where the second equality assumes a vertically isothermal disk. 
Protoplanetary disks have $\p_z\rhog<0$, thus stability against
convection ($N_z^2>0$) requires $\p_z\tepsilon <0 $. This is equivalent to
entropy increasing away from the midplane. A similar expression exists
for the radial buoyancy frequency $N_r$, but $|N_r|\ll |N_z|$ in thin,
smooth disks.

@@

Our equilibrium solutions satisfy the hydrostatic constraints of
Eq. \ref{steady_momr}---\ref{steady_momz} but are not in general
steady state solutions to the energy 
equation (\ref{eff_energy}), because the source term $\mathcal{C} \ne0$ for realistic disks.  
Limiting cases with $\mathcal{C} \equiv 0$ include \begin{inparaenum}[1)] 
\item 
  unstratified or 2D, razor-thin disk models with finite dust-gas drag; %(\S\ref{si});   
\item 
  perfectly-coupled dust with $\tstop=0$. %(\S\ref{results}). 
\end{inparaenum} 
The following analyses thus apply strictly to these limiting cases of
$\mathcal{C} = 0$ in equilibrium.  Our analysis is also a good approximation when 
$\tstop$ is sufficiently small such that the evolution of the background disk (e.g. dust-settling) 
occur on much longer timescales than the instabilities of interest.

>>>>

%\subsection{Dusty buoyancy forces}
We can now define the vertical buoyancy frequency $N_z$ of the mixture
as    
%$N_z$ of the mixture is given by 
\begin{align}
  N_z^2 \equiv - \frac{1}{\rho}\frac{\p P}{\p z}\frac{\p \seff}{\p z}
  =c_s^2(r) \frac{\p \ln{\rhog}}{\p z}\frac{\p \tepsilon}{\p z},
%  \quad 
 % N_z^2 \equiv - \frac{1}{\rho}\frac{\p P}{\p z}\frac{\p \seff}{\p z}.
%&=
  %\frac{c_s^2(r)}{\left(1+\epsilon\right)^2}\frac{\p\ln\rhog}{\p 
%  z}\frac{\p\epsilon}{\p z} \\ &
  %                                =
 % \frac{\epsilon}{\left(1+\epsilon\right)^2}\left(\frac{z}{\Htilde}\right)^2\OmK^2\notag,  
\end{align}
%Typically in a thin, smooth disk we have $|N_r|\ll |N_z|$. 
where the second equality assumes a vertically isothermal disk. 
Protoplanetary disks have $\p_z\rhog<0$, thus stability against vertical 
convection ($N_z^2>0$) requires $\p_z\tepsilon <0 $, i.e. the dust density drops faster 
than the gas density away from the midplane. 
This is equivalent to 
entropy increasing away from the midplane. A similar expression exists
for the radial buoyancy frequency $N_r$, but $|N_r|\ll |N_z|$ in thin,
smooth disks.

@@

Our equilibrium solutions satisfy the hydrostatic constraints of
Eq. \ref{steady_momr}---\ref{steady_momz} but are not in general
steady state solutions to the energy 
equation (\ref{eff_energy}), because the source term $\mathcal{C} \ne0$ for realistic disks.  
Limiting cases with $\mathcal{C} \equiv 0$ include \begin{inparaenum}[1)] 
\item 
  unstratified or 2D, razor-thin disk models with finite dust-gas drag; %(\S\ref{si});   
\item 
  perfectly-coupled dust with $\tstop=0$. %(\S\ref{results}). 
\end{inparaenum} 
The following analyses thus apply strictly to these limiting cases of
$\mathcal{C} = 0$ in equilibrium.  Our analysis is also a good approximation when 
$\tstop$ is sufficiently small such that the evolution of the background disk (e.g. dust-settling timescales) 
occur on much longer timescales than the dust dynamics of interest (e.g. instability growth timescales).
